---
title: "dd_project_v2"
author: "nehali"
date: "24/03/2020"
output: html_document
---
```{r}
library(tidyverse)
library(janitor)
library(readxl)
```



/* TASK-1 */

```{r}
decathalon <- readRDS("dd_project_data/decathlon.rds")
decathalon
```

```{r}
decathalon_clean <- clean_names(decathalon)
decathalon_clean

```

```{r}
decathalon_reform <-decathalon_clean %>%
  rownames_to_column("surname") %>%
    rename(
    run_100m = x100m,
    rum_400m = x400m,
    hurdle_110m = x110m_hurdle,
    run_1500m = x1500m,
    javelin = javeline
  ) %>%
    mutate(
      surname = tolower(surname),
      competition = as.character(competition)
    ) %>%
    pivot_longer(run_100m:run_1500m, names_to = "event", values_to = "score")
  
  
```

# writing clean data to csv

```{r}
write_csv(decathalon_reform, "clean_data/decathalon_clean.csv")
```

```{r}
decathalon_reform <- decathalon_clean %>% rownames_to_column()
```

/* Who had the longest long jump seen in the data? */

```{r}
decathalon_reform %>%
  arrange(desc(long_jump)) %>%
  head(1)
  
```

/*   What was the average 100m time in each competition? */
```{r}
decathalon_reform %>%
  group_by(competition) %>%
  summarise(avg_time = mean(x100m))
```

/*3. Who had the highest total points across both competitions? */
```{r}
decathalon_reform %>%
  distinct(rowname, competition,points) %>%
  group_by(rowname) %>%
  summarise(points_total = sum(points)) %>%
  arrange(desc(points_total)) %>%
  head(1)
```
/*4.What was the shot-put scores for the top three competitors in each competition? */
```{r}
decathalon_reform %>%
  select(shot_put, rank, competition) %>%
  filter(rank <= 3)
```

/*5-What was the average points for competitors who ran the 400m in less than 50 seconds vs. those than ran 400m in more than 50 seconds?*/


```{r}
decathalon_reform %>%
  
  filter(x400m < 50) %>%
  mutate(fast_400 = x400m < 50) %>%
  group_by(fast_400) %>%
  summarise(avg_points = mean(points))

 
  
```

/* TASK-4 */



```{r}
candy_2015 <- read_excel("raw_data/boing-boing-candy-2015.xlsx")
candy_2016 <- read_excel("raw_data/boing-boing-candy-2016.xlsx")
candy_2017 <- read_excel("raw_data/boing-boing-candy-2017.xlsx")
```
/* data cleaning */

```{r}
candy_2015 <- clean_names(candy_2015)
candy_2016 <- clean_names(candy_2016)
candy_2017 <- clean_names(candy_2017)
```

/*remove prefix from col names of candy_2017 */

```{r}
names(candy_2017) <- str_remove(names(candy_2017), "q[0-9]+_")
```


# Add an id number to keep track entries when make long format
# convert to desired long format and adding columns 'gender' and 'country' so can bind to 2017
# also add a year column so that know which year the data comes from when bind all sets together


```{r}
candy_2015_clean <- candy_2015 %>%
  mutate(person_id = row_number()) %>%
  pivot_longer(x100_grand_bar:york_peppermint_patties, names_to = "candy", values_to = "rating")
mutate(year = 2015,
       gender = NA,
       country = NA
       ) %>%
  select(year, person_id, going_out = are_you_actually_going_trick_or_treat_yourself,
         )
```




