---
title: "R Notebook"
output: html_notebook
---

# the RPostgreSQL package contains the specific drivers for connecting to PostgreSQL databases
library(RPostgreSQL)
# first, let's get our credentials from the local keyring
keyring_unlock(keyring = "local")
username <- key_get(service = "postgresql_username", keyring = "local")
password <- key_get(service = "postgresql_password", keyring = "local")
keyring_lock(keyring = "local")
# next, we create a connection to the database
my_db_connection <- dbConnect(drv = PostgreSQL(max.con = 1), user = username, password = password, dbname='omni_employees', host='localhost')

```{r}
keyring_unlock(keyring = "remote")
```
```{r}
username <- key_get(service = "omni_postgresql_username", keyring = "remote")
```
```{r}
password <- key_get(service = "omni_postgresql_password", keyring = "remote")
```
```{r}
keyring_lock(keyring = "remote")
```
```{r}
my_db_connection <- dbConnect(drv = PostgreSQL(max.con = 1), user = username, password = password, dbname='mvhbdgdk', host='34.245.37.126')
```

```{r}
data <- dbGetQuery(conn = my_db_connection,
                   statement = 
                     "SELECT * FROM wrestlers"
                   )
```

```{r}
dbListTables(conn = my_db_connection)
```
£# gives names of all,the cols
```{r}
dbListFields(conn = my_db_connection, name = "wrestlers")
```

```{r}

```



#CLOSE DB CONNECTION
```{r}

  dbDisconnect(my_db_connection)

```




