---
title: "WK_HW_W6"
author: "nehali"
date: "17/04/2020"
output: html_document
---



```{r}
library(tidyverse)
library(ggplot2)
library(CRANsearcher)
```

```{r}
msleep

```
```{r}
jabb <- msleep %>%
  
  filter(!is.na(name)) %>%
  group_by(name == "Jabberwockies") %>%
  summarise(mean = mean(sleep_total))

jabb


```


u =10.433, mean_sleep_total
```{r}
mean(msleep$sleep_total)
```
population mean = 10.433

#observed stat
```{r}
observed_stat <- msleep %>%
  summarise(mean_sleep = mean(sleep_total))
observed_stat

```



```{r}
msleep %>%
  ggplot(aes(x = sleep_total, bins = 10)) +
  geom_bar()
```

alpha = 0.05, 
mean_sleep_total = 10.433
#Perform an appropriate statistical test to determine whether omnivores sleep for significantly longer than herbivores, on average.

Ho-> avg sleep omni > avg sleep herb
H1 -> avg sleep omni < avg sleep herb

```{r}
null_dis <- msleep %>%
specify(response = sleep_total)%>%
  hypothesize(null = "point", mu = 10.433) %>%
  generate(reps = 100, type = "bootstrap") %>%
calculate(stat = "mean")
```

#1.2 
```{r}
null_dis  %>%
  visualise(bins = 30)
```

#visualizing observerd stat

```{r}
observed_stat
```

```{r}
null_dis %>%
  visualise(bins = 30) +
  shade_p_value(obs_stat = observed_stat$mean_sleep, direction = "both")
```
#p value
```{r}
p_value <- null_dis%>%
  get_p_value(obs_stat = observed_stat$mean_sleep, direction = "both")
p_value
```
(iv) proportion

Perform an appropriate statistical test to determine whether the proportion of domesticated animal types in the population of animal types is greater than 5%.
[Hint - think about creating an is_domesticated variable for the analysis]

```{r}
nulldis<- msleep %>% 
  mutate(is_domesticated = ifelse(conservation == "domesticated", TRUE, FALSE)) %>%  
  filter(na.rm == FALSE) %>%
  summarise("is_domesticated" == TRUE) 

  specify(response = conservation, success = "domesticated") %>% 
  hypothesize(null = "point") %>% 
 generate(reps = 1000, type = "permute") %>% 
  calculate(stat = "diff in prop", order = c("domesticated"))
```

```{r}
nulldis
```



#1.2 Hypothesis testing interpretation

1. alpha - 0.40
Ho :Uo = 0.40
Ha : Uo != 0.40
Null hypothesis would be 40% are already aware
Alternate hypothesis would be they are not aware
Method used : Bootstrapping

2. Ho : Right hand side
Ha : Top of the page
stat = prop
method : bootstrap

3. Permutation


#1.2.2

1. significance level = 0.05, p-value = 0.07

accept null hypothesis

2. significance level:0.01, p- value :0.006
the stronger the evidence that we can reject the null hypothesis.

3. signi level:0.05, p value: 0.55

Accept null hypothesis

2.1 MARKET BASKET ANALYSIS



