---
title: "R Notebook"
output: html_notebook
---

#MVP

2.2.1-> Write a function which multiples all numbers by 15 and adds 4.

```{r}
multiply_15_add_4 <- function(x){
  return(x*15+4)
}

```

```{r}
multiply_15_add_4 ( x = 1 )
multiply_15_add_4( x = 2 )
multiply_15_add_4( x = 3)
```

2.2.2 -> Write a function that returns “bird”, if the input is “goose”, “duck” or “pigeon”, and returns “not bird” for all other input.

```{r}
is_bird  <- function(x) 
  {
  if ( x%in%  c("goose", "duck", "pigeon")) 
    {
    return("is_bird")

} else {
  return("not_bird")
}
}
```

2.2.3

```{r}
multiply_by_10 <- function(x)
{
  if ( is.numeric(x)) {
       return(x * 10)
  } else {
    return("invalid output")
  }
}
```
```{r}
multiply_by_10( x=2 )
multiply_by_10( x=7 )
multiply_by_10( x=5.3)
multiply_by_10( x = "a" )
```

2.3 ifelse, recode, when

2.3.1
```{r,echo = TRUE}
# ifelse
sizes <- c(13, 15, 10, 8, 22)

ifelse(sizes > 10, "big", "small")

#case_when
dplyr::case_when (sizes > 10 ~ "big",
  TRUE ~ "small")

 #recode

dplyr :: recode(sizes, '10' = "small", '8' = "small", default = "big")

```

2.3.2

```{r}
fruit <- c("apple", "apple", "banana", "cherry", "cherry")

```
#ifelse
```{r}
animals <- c("alpaca", "bonobo", "chipmunk")
animals <- ifelse(fruit == "apple", "alpaca", fruit)
animals <- ifelse(fruit == "banana", "bonobo", animals)
animals <- ifelse(fruit == "cherry", "chipmunk", animals)
animals
```


#case when

```{r, warning=FALSE, message=FALSE}
library(dplyr)
```

```{r}
animals <- c("alpaca", "bonobo", "chipmunk")
animals <- case_when(
  fruit == "apple" ~ "alpaca",
                     fruit == "banana" ~ "bonobo",
                     fruit == "cherry" ~ "chipmunk" )
animals
```

2.3.3 

```{r}
wife_age <- c(29L, 30L, 36L, 31L, 22L)
husband_age <- c(28L, 35L, 32L, 31L, 29L)
```
#ifelse
```{r}
ifelse(wife_age > husband_age, "wife older", ifelse(wife_age < husband_age, "husband older", "same_age"))
```
#case_when

```{r}
case_when(wife_age > husband_age ~ "wife older",
          wife_age < husband_age ~ "husband older",
          wife_age == husband_age ~ "same age"
          )
```

#recode

```{r}
difference <- sign( husband_age - wife_age)
recode(difference, '-1' = "wife older", '0' = "same age", '1' = "husband older")
```


2.4 loops

```{r}
my_list <- list(
  4,
  "apple",
  10.5,
  c("is", "an", "apple"),
  "apple",
  c("i", "like", "apples"),
  8
)
my_list
```
Use a loop to print out every element of `my_list` which is of type `character`. Decide if you need a `for` loop or a `while` loop.

```{r}

for(element in my_list) {
  if(is.character(element)) {
    print(element)
  }
}
```
2.4.2
Once again write a loop that prints out character elements. This time if the element has a length() greater than one, paste() all the elements in that vector together into one big character vector.

```{r}
for(element in my_list) {
  if(is.character(element)) {
    
    if(length(element) > 1) {
      
      print(paste(element, collapse = " "))
            } else {
              print(element)
            }
      }
   }
```

EXTENSION

Write code that prints a multiplication table for numbers up to 12. i.e. there will be 12 rows and 12 columns, and each element should be the row number multiplied by the column number.

```{r}
matrix(1:12)  %*%  t(matrix(1:12))

matrix
```
3.2. Write a function that takes a vector, and creates a text art histogram, like the one below.

You may want to use the function `cat()`. This is similar to `print()`, but prints directly, without vector markers. You can also include newlines `"\n"` when using `cat()`.

```
1 | ***
2 | *
3 | *******
4 | ****
5 | **
```

```{r}
create_histogram <- function(x) {
  
  distinct <- sort(unique(x))
  
  for (i in distinct){
    
    count <- sum(x == i)
    cat(i)
    cat('|')
    cat(rep("*", count))
    cat("\n")
    
  }
}
x
```

3.3
Write a guessing game where the user has to guess a secret number. After every guess the program tells the user whether their number was too large or too small. At the end the number of tries needed should be printed.

To take user input, use the function readline(). Whenever R encounters readline, the code will stop, and the value assigned from readline will depend on the value that the user inputs. For more information see the help file.

```{r}

```








