---
title: "strings_hw"
output: html_document
---
```{r}
tweets <- read.csv("data/code_clan_tweets.csv", stringsAsFactors=FALSE)
tweets
```
/*2.First, we’re going to summarise the number of likes (favorite_count) CodeClan tweets have. Create a boxplot to check for outliers.  */


```{r}
#boxplot(tweets %>% group_by(favourites_count)
tweets_sum <- group_by(tweets,favorite_count)
summarise <- count(tweets_sum)
summarise
boxplot(summarise$favorite_count)
```
/*3. Find the total number of favourited tweets (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).     */
```{r}
x <- sum(tweets$favorite_count > 0)
x
```
/* 4.  Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.   */
```{r}
tweets %>% group_by(source) %>% summarise(mean(retweet_count))

```

/*5.  Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.   */


```{r}
tweets %>% mutate(media_type = replace_na(media_type, "text")) %>% group_by(media_type) %>% summarise(sum(favorite_count))
#tweets %>% arrange(desc())%>%group_by(media_type) %>% sum(favorite_count)

```

/*6. Find the mean number of characters that a CodeClan tweet contains. */

```{r}
tweets_with_length <- tweets %>% mutate(string_length = str_length(text)) %>% mutate(string_length = replace_na(string_length, 0))
tweets_with_length
mean(tweets_with_length$string_length)
#mean(tweets_with_length$string_length, na.rm = TRUE)
```
/*7.   The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.  */
```{r}
codeclaninfo <- read.csv("data/code_clan_info.csv", stringsAsFactors=FALSE)
codeclaninfo
```
```{r}
joined <- tweets %>% left_join(codeclaninfo, by = c("tweet_id" = "tweet_id"))
joined

```
/*8.From your new joined data, create a new tibble codeclan_hashtags containing only the tweet_id and hashtags in lowercase for analysis. Keep only those tweets with hashtags.    */
```{r}
tibble <- joined %>% mutate(code_clan_hashtags = tweet_id$hashtags)
tibble
```

